---
title: "ambR_Toolbox_CSS_practice"
output: html_document
date: "2025-11-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is a practice exercise of the Chapter from Toolbox CSS written by Felix Lennert on 2023-01-16.

Note: When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
example <- matrix(sample(0:2, 10*10, replace = TRUE, prob = c(0.4, 0.3, 0.3)), ncol = 10) 
print(example)

# prob is normalized to 1; the number of prob vectors should be equal to number of elements

# find the frequency of value "1" in the 10*10 matrix 
sum(example[, 1] == 1)    # in the first column

# find the frequency of value "1" in all columns of a matrix
colSums(example == 1)

# Total sum of freuqencies of value "1"
sum(colSums(example == 1))
sum(colSums(example == 0))
sum(colSums(example == 2))

# the one below is for the values along the row
sum(example[1, ] == 1)

image(example, col = c("black","red","green"), axes = FALSE)
# the prob should sum to 1 (normalized to 1)
```

## Functions


```{r pressure, echo=FALSE}
sum_numbers <- function(a, b) {
  return(a + b)
}
sum_numbers(5, 3)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
